The Nature and Orbit of the Ophiuchus Stream

### 2015-01-03 tex/ms.tex
Added Heather Flewelling to the author list. Added a new online-only table (Table 5, table5.tex) that lists lines used in element abundance analysis.

\author{Branimir Sesar\altaffilmark{1,2}}
\author{Jo Bovy\altaffilmark{3,4}}
\author{Edouard J.~Bernard\altaffilmark{5}}
\author{Nelson Caldwell\altaffilmark{6}}
\author{Judith G.~Cohen\altaffilmark{7}}
\author{Morgan Fouesneau\altaffilmark{1}}
\author{Christian I.~Johnson\altaffilmark{6}}
\author{Melissa Ness\altaffilmark{1}}
%\author{Maria Bergemann\altaffilmark{1}}
\author{Annette M.~N.~Ferguson\altaffilmark{5}}
\author{Nicolas F.~Martin\altaffilmark{8,1}}
\author{Hans-Walter Rix\altaffilmark{1}}
\author{Edward F.~Schlafly\altaffilmark{1}}
%\author{builders}
\author{William S.~Burgett\altaffilmark{15}}
\author{Kenneth C.~Chambers\altaffilmark{9}} 
%\author{L.~Denneau\altaffilmark{9}} 
%\author{P.~Draper\altaffilmark{10}} 
%\author{H.~Flewelling\altaffilmark{9}} 
%\author{T.~Grav\altaffilmark{11}} 
%\author{J.~N.~Heasley\altaffilmark{9}} 
\author{Klaus W.~Hodapp\altaffilmark{9}} 
%\author{M.~E.~Huber\altaffilmark{9}} 
%\author{R.~Jedicke\altaffilmark{9}} 
\author{Nick Kaiser\altaffilmark{9}} 
%\author{R.-P.~Kudritzki\altaffilmark{9}}
%\author{G.~A.~Luppino\altaffilmark{9}}
%\author{R.~H.~Lupton\altaffilmark{12}}
\author{Eugene A.~Magnier\altaffilmark{9}}
\author{Imants Platais\altaffilmark{11}}
%\author{N.~Metcalfe\altaffilmark{10}}
%\author{D.~G.~Monet\altaffilmark{13}}
%\author{J.~S.~Morgan\altaffilmark{9}}
%\author{P.~M.~Onaka\altaffilmark{9}}
%\author{P.~A.~Price\altaffilmark{12}}
%\author{C.~W.~Stubbs\altaffilmark{14}}
%\author{W.~Sweeney\altaffilmark{9}}
\author{John L.~Tonry\altaffilmark{9}}
%\author{R.~J.~Wainscoat\altaffilmark{9}}
\author{Christopher Waters\altaffilmark{9}}
\author{Rosemary~F.~G.~Wyse\altaffilmark{11}}

@@

We determined stellar parameters from the continuum-normalised, radial
velocity-corrected spectra using the SMH code of \citet{cas14}, which is built
on the MOOG code of \citet{sne73}. Kurucz $\alpha-$enhanced (0.4 dex) model
atmospheres \citep{ck04} and a line list compiled from \citet{fre10} by
\citet{cas14} were used (see Table~\ref{lines}). First, effective temperatures
were calculated from 2MASS photometry and color-temperature calibrations of
\citet{ghb09} and spectroscopic temperatures were optimized around this value
using the SMH code, by removing abundance trends with line excitation potential.
Parameters of $\log g$ and ${\rm [Fe/H]}$ were determined using 14 Fe I and 2-3 
Fe II lines to achieve ionization balance, and microturbulence was calculated by
removing abundance trends with reduced equivalent width of the lines. Estimates 
of the $\alpha-$enhancement were obtained using only the few available clean Mg,
Ca and Ti (I and II) lines, which comprised a total of 6-8 lines per star. The
abundances were measured from equivalent widths and the lines we used are listed
in Table~\ref{lines}. Because Mg lines are strong and may be saturated, the
values of ${\rm [Mg/Fe]}$ are significantly different than values of
${\rm [Ca/Fe]}$ and ${\rm [Ti/Fe]}$.

@@

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\scriptsize}
\setlength{\tabcolsep}{0.02in}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{Element abundances of Ophiuchus stream stars\label{table_abundances}}
\tablehead{
\colhead{Name} & \colhead{$T_{eff}$} & \colhead{$\log g$} &
\colhead{${\rm [Fe/H]}$} & \colhead{${\rm [Mg/Fe]}$} &
\colhead{${\rm [Ca/Fe]}$} & \colhead{${\rm [Ti/Fe]}$}  \\
\colhead{ } & \colhead{(K)} & \colhead{(dex)} &
\colhead{(dex)} & \colhead{(dex)} & \colhead{(dex)} &
\colhead{(dex)}
}
\startdata
rgb1 & 5680 & 3.0 & -1.95 & -0.2 & 0.6 & 0.6 \\
rgb2 & 5450 & 2.8 & -2.02 &  0.1 & 0.6 & 0.3 \\
rgb3 & 5700 & 3.0 & -1.95 &  0.2 & 0.3 & 0.5 \\
rgb4 & 5500 & 2.8 & -1.95 &  0.3 & 0.6 & 0.6 \\
rgb5 & 5720 & 3.4 & -1.90 &  0.0 & 0.7 & 0.5 
\enddata
\tablecomments{The uncertainty in $T_{eff}$ is $<200$ K, $<0.4$ dex for
$\log g$, $\lesssim0.2$ dex for ${\rm [Fe/H]}$, and $\sim0.3$ dex for abundances
of $\alpha-$elements.}
\end{deluxetable}

@@

As shown by \citet{sb13}, the velocity dispersion of the progenitor scales with the 
mass of the progenitor as $\sigma_v \propto M_{dyn}^{1/3}$. In {\em galpy}, the
model used for stream generation was calibrated using a progenitor of mass
$M_{dyn}=2\times10^4$ $M_\sun$. The stream formed by the tidal disruption of this progenitor could be modeled with $\sigma_v=0.365$ km s$^{-1}$ \citep{bov14}. Using
the above scaling relation and $\sigma_v = 0.4$ km s$^{-1}$, we find that the progenitor of the Ophiuchus stream
had a mass of $M_{dyn}\sim2\times10^4$ $M_\sun$.

>>>>

\author{Branimir Sesar\altaffilmark{1,2}}
\author{Jo Bovy\altaffilmark{3,4}}
\author{Edouard J.~Bernard\altaffilmark{5}}
\author{Nelson Caldwell\altaffilmark{6}}
\author{Judith G.~Cohen\altaffilmark{7}}
\author{Morgan Fouesneau\altaffilmark{1}}
\author{Christian I.~Johnson\altaffilmark{6}}
\author{Melissa Ness\altaffilmark{1}}
%\author{Maria Bergemann\altaffilmark{1}}
\author{Annette M.~N.~Ferguson\altaffilmark{5}}
\author{Nicolas F.~Martin\altaffilmark{8,1}}
\author{Hans-Walter Rix\altaffilmark{1}}
\author{Edward F.~Schlafly\altaffilmark{1}}
%\author{builders}
\author{William S.~Burgett\altaffilmark{15}}
\author{Kenneth C.~Chambers\altaffilmark{9}} 
%\author{L.~Denneau\altaffilmark{9}} 
%\author{P.~Draper\altaffilmark{10}} 
\author{H.~Flewelling\altaffilmark{9}} 
%\author{T.~Grav\altaffilmark{11}} 
%\author{J.~N.~Heasley\altaffilmark{9}} 
\author{Klaus W.~Hodapp\altaffilmark{9}} 
%\author{M.~E.~Huber\altaffilmark{9}} 
%\author{R.~Jedicke\altaffilmark{9}} 
\author{Nick Kaiser\altaffilmark{9}} 
%\author{R.-P.~Kudritzki\altaffilmark{9}}
%\author{G.~A.~Luppino\altaffilmark{9}}
%\author{R.~H.~Lupton\altaffilmark{12}}
\author{Eugene A.~Magnier\altaffilmark{9}}
\author{Imants Platais\altaffilmark{11}}
%\author{N.~Metcalfe\altaffilmark{10}}
%\author{D.~G.~Monet\altaffilmark{13}}
%\author{J.~S.~Morgan\altaffilmark{9}}
%\author{P.~M.~Onaka\altaffilmark{9}}
%\author{P.~A.~Price\altaffilmark{12}}
%\author{C.~W.~Stubbs\altaffilmark{14}}
%\author{W.~Sweeney\altaffilmark{9}}
\author{John L.~Tonry\altaffilmark{9}}
%\author{R.~J.~Wainscoat\altaffilmark{9}}
\author{Christopher Waters\altaffilmark{9}}
\author{Rosemary~F.~G.~Wyse\altaffilmark{11}}

@@

We determined stellar parameters from the continuum-normalised, radial
velocity-corrected spectra using the SMH code of \citet{cas14}, which is built
on the MOOG code of \citet{sne73}. Kurucz $\alpha-$enhanced (0.4 dex) model
atmospheres \citep{ck04} and a line list compiled from \citet{fre10} by
\citet{cas14} were used (see Table~5 in the electronic version of the Journal).
First, effective temperatures were calculated from 2MASS photometry and
color-temperature calibrations of \citet{ghb09} and spectroscopic temperatures
were optimized around this value using the SMH code, by removing abundance
trends with line excitation potential. Parameters of $\log g$ and ${\rm [Fe/H]}$
were determined using 14 Fe I and 2-3 Fe II lines to achieve ionization balance,
and microturbulence was calculated by removing abundance trends with reduced
equivalent width of the lines. Estimates of the $\alpha-$enhancement were
obtained using only the few available clean Mg, Ca and Ti (I and II) lines,
which comprised a total of 6-8 lines per star. The abundances were measured from
equivalent widths and the lines we used are listed in Table~5. Because Mg lines
are strong and may be saturated, the values of ${\rm [Mg/Fe]}$ are significantly
different than values of ${\rm [Ca/Fe]}$ and ${\rm [Ti/Fe]}$.

@@

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\scriptsize}
\setlength{\tabcolsep}{0.02in}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{Element abundances of Ophiuchus stream stars\label{table_abundances}}
\tablehead{
\colhead{Name} & \colhead{$T_{eff}$} & \colhead{$\log g$} &
\colhead{${\rm [Fe/H]}$} & \colhead{${\rm [Mg/Fe]}$} &
\colhead{${\rm [Ca/Fe]}$} & \colhead{${\rm [Ti/Fe]}$}  \\
\colhead{ } & \colhead{(K)} & \colhead{(dex)} &
\colhead{(dex)} & \colhead{(dex)} & \colhead{(dex)} &
\colhead{(dex)}
}
\startdata
rgb1 & 5680 & 3.2 & -2.00 & -0.12 & 0.63 & 0.69 \\
rgb2 & 5430 & 3.3 & -1.95 &  0.06 & 0.62 & 0.47 \\
rgb3 & 5700 & 3.1 & -1.95 &  0.23 & 0.27 & 0.46 \\
rgb4 & 5400 & 2.8 & -1.90 &  0.24 & 0.57 & 0.42 \\
rgb5 & 5720 & 2.9 & -1.90 & -0.14 & 0.83 & -- 
\enddata
\tablecomments{The uncertainty in $T_{eff}$ is $<200$ K, $<0.45$ dex for
$\log g$, $\lesssim0.2$ dex for ${\rm [Fe/H]}$, and $\sim0.35$ dex for
abundances of $\alpha-$elements.}
\end{deluxetable}

@@

As shown by \citet{sb13}, the velocity dispersion of the progenitor scales with
the mass of the progenitor as $\sigma_v \propto M_{dyn}^{1/3}$. In {\em galpy},
the model used for stream generation was calibrated using a progenitor of mass
$M_{dyn}=2\times10^4$ $M_\sun$. The stream formed by the tidal disruption of
this progenitor could be modeled with $\sigma_v=0.365$ km s$^{-1}$
\citep{bov14}. Using the above scaling relation and $\sigma_v=0.4$ km s$^{-1}$,
we find that the progenitor of the Ophiuchus stream had a mass of
$M_{dyn}\sim2\times10^4$ $M_\sun$.
